---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# shortuuid

<!-- badges: start -->
[![R-CMD-check](https://github.com/schochastics/shortuuid/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/schochastics/shortuuid/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of shortuuid is to generate and translate standard UUIDs into shorter - or just different - formats and back.
Inspired by [short-uuid](https://www.npmjs.com/package/short-uuid) and a post on [fosstodon](https://fosstodon.org/@josi/112978240064605859)

## Installation

You can install the development version of shortuuid like so:

``` r
remotes::install_github("schochastics/shortuuid")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(shortuuid)
# generate random uuids
ids <- generate_uuid(n = 5)
ids
is.uuid(ids)

# alphabet: "123456789ABCDEFGHJKLMNPQRSTUVWXYZabcdefghijkmnopqrstuvwxyz"
b58 <- uuid_to_bitcoin58(ids)
b58

# alphabet: "123456789abcdefghijkmnopqrstuvwxyzABCDEFGHJKLMNPQRSTUVWXYZ"
f58 <- uuid_to_flickr58(ids)
f58
# convert back
bitcoin58_to_uuid(b58)
flickr58_to_uuid(f58)
```

## Addendum

Code to generate uuids taken from [@rkg8](https://github.com/rkg82/uuid-v4)
